---
title: "Lab 00 - Hello IDS!"
author: "Rudy Adair"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(shiny)
library(randomcoloR)
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Rudy", "Herman", "Abdul", 
           "Matt", "Hamish"),
  github_username = c("rudyadair", "herman", "7aman4013", 
                      "matthurrell", "hamlot12"), 
  colour = c("powderblue", "peachpuff2", "lightgoldenrod2", 
             "darkorchid", "bisque"),
  hobby = c("Cricket", "Climbing", "maths/coding", 
            "Badminton", "Golf"),
  favourite_number = c(5, 6, sample(10, size=1), 9, 1)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


A graph of our usernames with our favourite number, coloured by our favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favourite Number",
          title = "Trendsetters")
```

The labs() function allows you to edit different misc options in a graph.

### Exercise 20

```{r new-bar-plot}

color = c(randomColor(), randomColor(), randomColor(), randomColor(), randomColor())

p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar(fill = sample(color, 5))
p2
```

Only approximately 1 entry per bar doesn't create a useful graph.
